On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
Cosmetic fixes

Taking the examples into consideration,
we can conjecture that there is an infinite set with rational distances
that contains $\mathcal{P_48}$.
(However, it is known that\cite{solymosi2010question}
if a rational set S has infinitely many points on a line or on a circle,
then all but 4 resp. 3 points of S are on the line or on the circle.)

@@

Note that distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{1767}{2} - \frac{340}{2}\right)^2 + \left(\frac{147}{2}\right)^2\cdot143} = 2\sqrt{320401}
\end{equation}

Where 320401 is prime.

@@

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search an intuition of the authors;

The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo

>>>>

Taking the examples into consideration,
we can conjecture that there is an infinite set with rational distances
that contains $\mathcal{P_48}$.
(However, it is known~\cite{solymosi2010question} that
if a rational set $S$ has infinitely many points on a line or on a circle,
then all but 4 resp. 3 points of $S$ are on the line or on the circle.)

@@

Note that distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{1767}{2} - \frac{340}{2}\right)^2 + \left(\frac{147}{2}\right)^2\cdot143} = 2\sqrt{320401}
	.
\end{equation}
It's notable that 320401 is a prime number.

@@

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search an intuition of the authors.
The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo
